Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

### 2019-11-14 manuscript/manuscript.Rmd
Added rough draft of Methods section

Conjoint analysis forces a consumer to choose between alternatives, revealing which components of a choice are the most important to that consumer. Conjoint analysis has been widely used within social sciences to explain causality and has recently begun to be used in political and public policy fields. Helfer (2016) and Mummolo (2016) both used conjoint analysis to assess consumer perceptions of political communications. Conjoint is key in political research because it captures multidimensional causal relations.

>>>>

Conjoint anlysis is a common research method used to evaluate which attributes of a choice are most important to a consumer. A conjoint analysis survey includes sets of alternatives that consumers must choose between. These choice sets are made up of attributes such as price, brand, and features. However, the alternatives have different levels within these attributes. Price may be 20 dollars for Option A and 30 dollars for Option B, however Option A may not include a specific feature while Option B does.

Conjoint analysis reflects a real world experience where the consumer has to weigh tradeoffs and choose between alternatives. This reveals which components of a choice are the most important to that consumer. Aggregated results from all participants show which attributes have the greatest weight on a decision. Further insights can be concluded by analyzing responses of specific groups (i.e. according to gender, age, member of an organization).

Conjoint analysis has been widely used within social sciences to explain causality and has recently begun to be used in political and public policy fields. Helfer (2016) and Mummolo (2016) both used conjoint analysis to assess consumer perceptions of political communications. Conjoint is key in political research because it captures multidimensional causal relations.
